---
title: "Conditional and Joint Probability"
author: "Barraza Torres Jesús Daniel"
date: "`r Sys.Date()`"
output:
  word_document: default
  pdf_document: default
---

## Exercise 1

A small survey was conducted with 50 people regarding whether they own a car and whether they have a driver's license.

### Data (Example)

You can modify the values below or use the following as an example to work with:

```{r}
# Example frequency table:
datos <- data.frame(
  car = rep(c("Si", "Si", "No", "No"), 1),
  licence = rep(c("Si", "No", "Si", "No"), 1),
  frequency = c(20, 15, 5, 10)
)

# Total people
total <- sum(datos$frequency)
cat("Total people: ", total)
```

1. Joint probability that a person has a car and a driver's license.
```{r}
#Sum of cases (for later)
freq_both <- datos$frequency[datos$car == "Si" & datos$licence == "Si"]
joint_prob <- freq_both / total

#Probability
cat("Probability that a person has both car and license: ", joint_prob*100, "%")
```

2. Conditional probability that a person has a driver's license given they have a car.
```{r}
#Sum of cases (for later)
freq_car <- sum(datos$frequency[datos$car == "Si"])
freq_license <- sum(datos$frequency[datos$licence == "Si"])

#Probability
prob_cartolicense <- (freq_both/freq_car)
cat("Total people who has a licence given they have a car: ", prob_cartolicense*100, "%")
```

3. Conditional probability that a person has a car given they have a driver's license.
```{r}
#Probability
prob_licensetocar <- (freq_both/freq_license)
cat("Total people who has a licence given they have a car: ", prob_licensetocar*100, "%")
```

4. Check whether owning a car and having a driver's license are independent events.
```{r}
#Probability
prob_car=freq_car/total
prob_licence=freq_license/total

#If because why not
if (prob_car == prob_licensetocar & prob_licence == prob_cartolicense) {
  cat("The events are independent")
} else {
  cat("The events are dependent")
}
```

5. Create a Venn diagram representing the sets from the exercise and their intersection 
```{r}
library(VennDiagram)

venn.plot <- draw.pairwise.venn(
             area1 = freq_car,
             area2 = freq_license,
             cross.area = freq_both,
             category = c("Car", "License"),
             fill = c("#953472", "#126593" ),
             ity = "black",
             cex = 2,
             cat.cex = 2,
             cat.col = c("#311225", "#063045")
             )
```

